---
title: "Stat 3202 Lab 2"
author: "Linlin Xia"
date: "1/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Part a)
```{r}
NMC <- 10000
x_mean <- rep(NA, NMC)
x_var <- rep(NA, NMC)

for (i in 1:NMC) {
  temp_c <- rpois(10,2)
  temp_mean <- mean(temp_c)
  x_mean[i] <- temp_mean
  temp_var <- var(temp_c)
  x_var[i] <- temp_var
}

hist(x_mean)
hist(x_var)
```

Part b)
```{r}
print(mean(x_mean))
print(mean(x_var))
```
By counting the mean of both $\bar X$ and $s^2$ , we can find that they both close to the truth 2. So, using $\bar X$ is better because it shows normal distribution.

Part c)
```{r}
  running_MSE1<- var(x_mean)+(mean(x_mean)-2)^2
  running_MSE2 <- var(x_var)+(mean(x_var)-2)^2

print(running_MSE1)
print(running_MSE2)
```
It is better to choose $\hat{\lambda}$  = $\bar{X}$, beacuse the MSE of $\hat{\lambda}$ = $s^2$ is about five times of $\bar{X}$.

Part d)
I perfer $\hat{\lambda}$ = $\bar{X}$, because it has lower Mean squared error.

Part e)
```{r}
running_mean <- rep(NA, NMC)
running_var <- rep(NA, NMC)

running_temp <- rep(NA, NMC)

for(i in 1:NMC){
  running_temp[i] <- rpois(1,2)
  running_mean[i] <- sum(running_temp[1:i])/i
  running_var[i] <- var(running_temp[1:i])
}

plot(running_mean)
abline(h=2, col="red")
plot(running_var)
abline(h=2, col="red")
```

They are both converge to two as n increases.